\section{Equations of Order One}

\subsection{Separation of Variables}

We begin with equation*s of the form

\begin{equation*}
    Mdx+Ndy=0
\end{equation*}
where $M$ and $N$ can be multivariate of $x,y$.

It is separable iff
\begin{equation*}
    A(x)dx+B(y)dy=0.
\end{equation*}

Then find a function $F$ with total differential being the LHS of above, so $F=c$.

\subsection{Homogeneity}

\begin{definition}[Homogeneity of polynomials]
    Polynomials where all terms are of the same degree are homogeneous.
\end{definition}

Homoegeneity of functions is analogous to assigning physical dimensions (e.g. length) to all of the variables.
If the function has the length dimension to the $k$th power, then it is homogeneous of degree $k$.

\begin{example}
    If $x,y$ are lengths, then the following is homogeneous of degree 3.
    \begin{equation*}
        f(x,y)=2y^3\exp(\frac{y}{x})-\frac{x^4}{x+3y}
    \end{equation*}
\end{example}

Alternate definition also suffices for generality.

\begin{definition}[Homogeneous function]
    $f(x,y)$ is homogeneous of degree $k$ iff $f(\lambda x, \lambda y)=\lambda^kf(x,y)$.
\end{definition}

\begin{definition}[Alternate definition of homogeneity]
    If $f(x,y)$ can be rewritten as $f(\frac{y}{x})$ or $f(\frac{x}{y})$ then it is homogeneous.
\end{definition}

\subsection{Homogeneous Differential Equations}

\begin{theorem}[Homogeneous DEs]
    If $M(x,y)$ and $N(x,y)$ are homogeneous and of same degree, then $M(x,y)dx+N(x,y)dy=0$
    is a homogeneous DE.
\end{theorem}
    
\begin{theorem}[Homogeneous DEs]
    $M(x,y)/N(x,y)$ is homogeneous of degree 0.

    \begin{proof}
        If $M,N$ are homogeneous of some degree $n$, then
        \begin{eqnarray}
            M(x,y)=M(\lambda x,\lambda y)=\lambda ^nM(x,y)\\
            M(x,y)=N(\lambda x,\lambda y)=\lambda ^nN(x,y)
        \end{eqnarray}
        So for $M/N$,
        \begin{eqnarray}
            \frac{M(x,y)}{N(x,y)}=\lambda^0\frac{M(1,v)}{N(1,v)}
        \end{eqnarray}
        which is homogeneous of degree 0.
    \end{proof}
\end{theorem}

\begin{theorem}[Homogeneous DEs]
    If $f(x,y)$ is homogeneous of degree 0 in $x,y$, then $f(x,y)$ is a function of $y/x$ alone.
    \begin{proof}
        Let $y=vx$. Then, $f$ must be proven to be of $v$ alone. Substitute so that
        \begin{equation*}
            f(x,y)=f(x,vx)=x^0f(1,v)=f(1,v)
        \end{equation*}
    \end{proof}
\end{theorem}

\subsection{Homogeneous Coefficients}

Suppose coefficients $M,N$ in the equation*

\begin{equation*}
    M(x,y)dx+N(x,y)dy=0
\end{equation*}

are both homogeneous of same degree. So $M/N$ is a function of $y/x$ alone.
Can put in form using $y=vx$.
\begin{eqnarray}
    \frac{dy}{dx}+g(\frac{y}{x})=0\\
    x\frac{dv}{dx}+g(v)=0
\end{eqnarray}

This last equation* is separable.

\subsection{Exact Equations}

If there exists an equation* of the form $A(x)dx+B(y)dy=0$, the solution is a function with differential $A(x)dx+B(y)dy$.
Idea works for equation*s of form

\begin{equation*}
    dF=Mdx+Ndy.
\end{equation*}

So, $F(x,y)=c\implies dF=0$ and

\begin{equation*}
    Mdx+Ndy=0.
\end{equation*}

If there's a function $F$ such that $Mdx+Ndy$ is the \textbf{total differential}
of $F$, then Eq. 5 is an \textit{exact equation*} by definition. Can rewrite the total differential from the chain rule:

\begin{equation*}
    dF=\frac{\partial F}{\partial x}dx+\frac{\partial F}{\partial y}dy.
\end{equation*}

So $M=\frac{\partial F}{\partial x},N=\frac{\partial F}{\partial y}$. We can take 2nd derivative to show these are equal because the partials are continuous (Clairaut's theorem).

\begin{eqnarray}
    \frac{\partial M}{\partial y}=\frac{\partial^2 F}{\partial y\partial x}\\
    \frac{\partial N}{\partial x}=\frac{\partial^2 F}{\partial y\partial x}.
\end{eqnarray}

\begin{definition}[Exactness]
    \begin{equation*}
        \frac{\partial M}{\partial y}=\frac{\partial N}{\partial x}.
    \end{equation*}
\end{definition}

\begin{proof}
    Let $\phi(x,y)$ be a function where $\frac{\partial \phi}{\partial x}=M$. $\phi$ is the function you get from integrating $Mdx$ wrt $x$ and holding $y$. Then

    \begin{equation*}
        \frac{\partial^2\phi}{\partial y\partial x}=\frac{\partial M}{\partial y}=\frac{\partial N}{\partial x}
    \end{equation*}

    Integrating both sides wrt $x$:

    \begin{equation*}
        \frac{\partial \phi}{\partial x}=N+B'(y)
    \end{equation*}

    where $B'(y)$ is the integration constant. Let

    \begin{equation*}
        F=\phi(x,y)-B(y)
    \end{equation*}

    such that 

    \begin{align*}
        dF&=\frac{\partial \phi}{\partial x}dx+\frac{\partial \phi}{\partial y}dy-B'(y)dy\\
        &=Mdx+\left[N+B'(y)\right]dy-B'(y)dy\\
        &=Mdx+Ndy
    \end{align*}
\end{proof}

\begin{example} We have the DE
    \begin{equation*}
        3x(xy-2)dx+(x^3+2y)dy=0.
    \end{equation*}

    Then, 

    \begin{equation*}
        \frac{\partial M}{\partial y}=3x^2,\frac{\partial N}{\partial y}=3x^2
    \end{equation*}

    The DE is exact, and $F=c$ is the solution.

    \begin{eqnarray}
        \frac{\partial F}{\partial x}=M=3x^2y-6x\\
        \frac{\partial F}{\partial y}=N=x^3+2y
    \end{eqnarray}

    Try to find $F$ from 18, integrate both sides wrt $x$ with an integration constant $T(y)$.

    \begin{equation*}
        F=x^3y-3x^2+T(y)
    \end{equation*}

    Using Eq. 19, can can find $\frac{\partial F}{\partial y}$ from Eq. 20 and equate:

    \begin{equation*}
        x^3+T'(y)=x^3+2y\implies T'(y)=2y
    \end{equation*}

    Because $F=c$ is the I.C., can conclude 

    \begin{equation*}
        T(y)=y^2
    \end{equation*}

    Thus,

    \begin{equation*}
        F=x^3y-3x^2+y^2\Leftrightarrow x^3y-3x^2+y^2=c
    \end{equation*}
\end{example}

\subsection{Linear Equations of Order 1}

If an equation* is not exact, can attempt to do so by multiplying DE by an integrating factor.

\begin{definition}[Linear DE of order 1]
    \begin{equation*}
        A(x)\frac{dy}{dx}+B(x)y=C(x)
    \end{equation*}
\end{definition}

Divide each side by $A(x)$ to obtain

\begin{equation*}
    \frac{dy}{dx}+P(x)y=Q(x)
\end{equation*}

Suppose there exists for Eq. 25 a I.F. $v(x)>0$. Then,

\begin{equation*}
    v(x)\left[\frac{dy}{dx}+P(x)y\right]=v(x)Q(x)
\end{equation*}

becomes exact, or of form $Mdx+Ndy=0$. Here,

\begin{eqnarray}
    M=vPy-vQ\\
    N=v
\end{eqnarray}

Because the requirement is $\frac{\partial M}{\partial y}=\frac{\partial N}{\partial x}$,

\begin{align*}
    vP&=\frac{dv}{dx}\\
    Pdx&=\frac{dv}{v}\\
    \ln v&=\int Pdx\\
    v&=\exp(\int Pdx)
\end{align*}

We can then multiply both sides of the DE by this I.F. One side of this eqn will be of the product rule form, the derivative of $y\exp (\int Pdx)$:

\begin{equation*}
    \exp(\int Pdx)\frac{dy}{dx}+P\exp(\int Pdx)y=Q\exp(\int Pdx)
\end{equation*}

\subsection{General Solution of a Linear Equation}

Given the original form

\begin{equation*}
    \frac{dy}{dx}+P(x)y=Q(x)
\end{equation*}

suppose $P$ and $Q$ are continuous on $x\in (a,b)$ and $x=x_0$ is such a number. $y=y_0$ satisfies the initial condition.
This sol'n satisfies Eq. 34 for all $x$ in the interval. Multiplying Eq. 34 by integrating factor $\exp(\int Pdx)$ gives

\begin{equation*}
    yv=\int vQ\:dx + c
\end{equation*}

Because $v\neq 0$,

\begin{equation*}
    y=v^{-1}\int vQ\: dx + cv^{-1}
\end{equation*}

Given any $x_0,y_0$ in the interval, can find $c$ s.t. the DE is satisfied.
Every eqn of above form will have $P,Q$ with common interval of continuity and a unique set of solutions with one I.C. obtained by using the integrating factor.
These solutions are unique, so any other method yields a solution that align*s with the general solution–all possible solutions satisfying the DE on $x\in (a,b)$.

\subsection{Application of Mixing Problem}

Strategy is to determine the differential equation* describing rate of change of a certain quantity, then finding the particular solution with some trivial IC.

\begin{example}
    100 liter tank contains 10 kg salt mixed with 60 liter water. Sol'n with concentration 0.1 $\frac{\mathrm{kg}}{\mathrm{liter}}$ flows in at rate 5 liters/min.
    Solution is well stirred (asume equal distribution), outflow rate of 3 liters/min. Need to find salt in tank when it is full.

    Note that the tank will become full, as $\mathrm{in}-\mathrm{out}>0$. Let $x$ be kg of salt.
    Then, inflow rate is $0.1 \frac{\mathrm{kg}}{\mathrm{liter}}\cdot 5\frac{\mathrm{liter}}{\mathrm{min}}=0.5\frac{\mathrm{kg}}{\mathrm{min}}$. Out is
    $x \frac{\mathrm{kg}}{60\;\mathrm{liter}}\cdot 3\frac{\mathrm{liter}}{\mathrm{min}}=\frac{x}{20}\frac{\mathrm{kg}}{\mathrm{min}}$. We then express the DE as

    \begin{equation*}
        \frac{dx}{dt}=0.5-\frac{x}{20}
    \end{equation*}

    Then just express in linear form, solve with I.F. method.
\end{example}

\begin{example}
    Initially 50 gallons of brine, 10 lb dissolved salt. Inflow of 2 lb salt/gal at 5 gal/min, outflow of 3 gal/min, but \textbf{mixture kept uniform}.

    Inflow is thus 10 lb/min, outflow is $\frac{3x}{50+2t}$ lb/min. Key here is that mixture concentration on outflow does not change, so the volume dynamically adapts for changing amount of salt.
    50 gallons initially, influx of 5 gal - 3 gal out $\implies 50+(5-3)t$.
    DE is thus

    \begin{equation*}
        \frac{dx}{dt}=10-\frac{3x}{50+2t}
    \end{equation*}
\end{example}

\subsection{Integrating Factor by Inspection}

By recognizing differentials in a problem, can find the integrating factor by inspection.

\begin{example}
    Given
    \begin{equation*}
        ydx+(x+x^3y^2)dy=0
    \end{equation*}
    the terms can be grouped by like degree so
    \begin{equation*}
        (ydx+xdy)+x^3y^2dy=0.
    \end{equation*}
    Can be rewritten as
    \begin{equation*}
        d(xy)+x^3y^2dy=0
    \end{equation*}
    then divide by $(xy)^3$ for it does not affect integrability of $d(xy)$ term but keeps function of $y$ with $dy$ term,
    \begin{equation*}
        \frac{d(xy)}{(xy)^3}+\frac{dy}{y}=0.
    \end{equation*}
    Integrating:
    \begin{align*}
        \int (xy)^{-3}d(xy)+\int \frac{dy}{y}&=0\\
        \frac{(xy)^{-2}}{-2}+\ln|y|=C\\
        Cy=\frac{(xy)^{-2}}{2}\\
        Cy(xy)^2=1
    \end{align*}
\end{example}

\subsection{Determining Complex Integrating Factors}

Let there be the DE

\begin{equation*}
    Mdx+Ndy=0.
\end{equation*}

Suppose $\exists u$, possibly of both $x,y$ that is an integrating factor such that

\begin{equation*}
    uMdx+uNdy=0
\end{equation*}

and for it to be exact,

\begin{equation*}
    \frac{\partial}{\partial y}(uM)=\frac{\partial}{\partial x}(uN)
\end{equation*}

so $u$ satisfies

\begin{eqnarray}
    u\frac{\pr M}{\pr y}+M\frac{\pr u}{\pr y}=u\frac{\partial N}{\partial x}+N\frac{\pr u}{\pr x}\\
    u(\frac{\pr M}{\pr y}-\frac{\pr N}{\pr x})=N\frac{\pr u}{\pr x}-M\frac{\pr u}{\pr y}.
\end{eqnarray}

This does not lead anywhere, so let $u$ be a function of $x$. Thus, $\pr u/\pr y=0,\pr u/\pr x=du/dx$.
So the above reduces to

\begin{equation*}
    u(\frac{\pr M}{\pr y}-\frac{\pr N}{\pr x})=N\frac{du}{dx}\Leftrightarrow \frac{1}{N}(\frac{\pr M}{\pr y}-\frac{\pr N}{\pr x})dx=\frac{du}{u}
\end{equation*}

and integrating factor is the following, assuming LHS of above is a function of $x$ or $y$ alone
\begin{eqnarray}
    u=\exp\left[\int f(x)dx\right]\;(\text{for $x$})\\
    u=\exp\left[\int -g(y)dy\right]\;(\text{for $y$})
\end{eqnarray}